### 2016-09-20 overlay_fs.tex
draf
fixed line numbers again

\textcolor{red}{SHOW NEW PARTITION TABLE HERE}

@@

\begin{lstlisting}[]
<@\textcolor{gray}{\$\{ROOTDIR\}/etc/fstab}@>
<@\textcolor{gray}{
----------------------------------------}
\Reactivatenumber @>
proc            /proc            proc    defaults          0       0
/dev/mmcblk0p1  /boot            vfat    defaults          0       2
/dev/mmcblk0p2  /                ext4    defaults,noatime  0       1
/dev/mmcblk0p3  /home            ext4    defaults,noatime  0       2
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

>>>>

%\textcolor{red}{SHOW NEW PARTITION TABLE HERE}

@@

\Suppressnumber\begin{lstlisting}[]
<@\textcolor{gray}{\$\{ROOTDIR\}/etc/fstab}@>
<@\textcolor{gray}{
----------------------------------------}
\Reactivatenumber @>
proc            /proc            proc    defaults          0       0
/dev/mmcblk0p1  /boot            vfat    defaults          0       2
/dev/mmcblk0p2  /                ext4    defaults,noatime  0       1
/dev/mmcblk0p3  /home            ext4    defaults,noatime  0       2
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}
